Procedural generation of levels for the angry birds videogame using evolutionary computation\\

### 2020-01-17 IEEE_ConferenceOnGames/wcci_2020.tex
Finishes state of the art

>>>>

It is also interesting how some authors take into account the dynamics of Angry Birds gameplay, where the {\em domino effect} makes a big structure tumble over: Abdullah et al. \cite{Abdullah2019} talk about ``Rube Goldberg machines''. This specific pattern (structures that can be destroyed with a single strike) makes them interesting, and also since they are designed from a series of pre-defined structures, stability is guaranteed. This approach is similar to other which use pre-defined patterns (such as a set of towers) to guarantee stability: Ferreira and Toledo \cite{ferreira2014search} use such approach, with predefined groups of elements stacked always in the same way to guarantee that stability. The authors proposed also Tanager \cite{8082517} which again uses different stacks to structure the level and the blocks used in it, but it also encodes empty stacks (which translate to gaps). This methodology gives much more variability. At the same time, the authors proposed new ways of evaluating the levels, including interacting with actual users.
